Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

Finally, we show that $h$ crosses $B_{\bm{t}}$, or equivalently: $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})] = [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item The fact of $h$ crossing $r'$ tells us $\xleft(h) < x_1 \leq x_2 < \xright(h)$. Since $r' = \gbot(B_{\bm{t}})$, we have the x-range of $B_{\bm{t}}$ is contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.
    \item Since $h$ crosses $r^*$, we have $y_h \in [y_1, \maxtop(r')]$. By the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. Therefore, $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}

>>>>

Finally, we show that $h$ crosses $B_{\bm{t}}$, or equivalently: $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$ and $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})] = [y_1, \ytop(B_{\bm{t}})]$.
\begin{itemize}
    \item The fact of $h$ crossing $r'$ tells us $\xleft(h) < x_1 \leq x_2 < \xright(h)$. Since $r' = \gbot(B_{\bm{t}})$, the x-range of $B_{\bm{t}}$ must be contained in $[x_1,x_2]$. Therefore, $\xleft(h) < \xleft(B_{\bm{t}}) \le \xright(B_{\bm{t}}) < \xright(h)$.

    \item The fact of $h$ crossing $r^*$ also tells us that $y_h \in [y_1, \maxtop(r')]$. Moreover, by the definition of $h$, we have $y_h \leq \ytop(B_{\bm{t}})$. It thus follows that $y_h \in [y_1, \ytop(B_{\bm{t}})]$.
\end{itemize}
